# How to set up Python in Rstudio
https://www.youtube.com/watch?v=OtINRCXprGg


```{r}

library(reticulate)
# install_miniconda() # Already installed.
```

Environments: How to segregate installations of Python. $ conda activate r-reticulate $ conda deactivate
This is apparently fairly common in Python and by fairly I mean very. 

Also see: https://support.rstudio.com/hc/en-us/articles/360023654474-Installing-and-Configuring-Python-with-RStudio

## Step one install python (done)

Why use Anaconda vs. Python? Python.org version is bare, but that might be a good thing. Anaconda has all the packages that you need numpy and matplotlib.

In Terminal console (not python)
brian$ virtualenv python

source /Users/brian/Library/r-miniconda/bin/activate

```{r}
# This might already be done.
# Should this last bit be /bin/python (or) python3? Yes it should be. Not /bin/conda
Sys.setenv(RETICULATE_PYTHON = "/Users/brian/Library/r-miniconda/bin/python")
# Silence. Good.
```

```{r}
use_python("/Users/brian/Library/r-miniconda/bin/python")
```

This doesn't seem to work. I'm not sure where or if it is creating anything.
```{r}
py_run_string("aa = 6", local = T) # Where does this go?
py_run_string("aa = 6", local = F)
py_run_string("print('Hello world')", local = T)
py_run_string("aa", local = T)
```

```{python}
bb = 66
print(bb)
```


